### 2018-11-29 2018_nips_vigil_poster/main.tex
vigil last update

\headerbox{Datasets - CLEVR and CoGenT}{name=dataset, column=1}{
The CLEVR task:
		\begin{figure}[H]
		\centering
		\includegraphics[width=0.35\textwidth]{../img/teaser.jpg}
	    \end{figure}

@@

\begin{description}
	\item[$\bullet$] The [Training] column indicates wall times and final accuracies on the training set.
	\item[$\bullet$] The [Fine-tuning] column reports the used sub-set (30k samples) and the final accuracies on this sub-set during training
	\item[$\bullet$] Experiments can be reproduced by following the \textbf{mi-prometheus}  documentation
\end{description}

@@

	\begin{figure}[H]
	\centering
				\includegraphics[width=0.65\textwidth]{../img/fail_mac_cogent_b_shape.png}

>>>>

\headerbox{Datasets - CLEVR and CoGenT}{name=dataset, column=1}{
The CLEVR task:
		\begin{figure}[H]
		\centering
		\includegraphics[width=0.31\textwidth]{../img/teaser.jpg}
	    \end{figure}

@@

\begin{description}
	\item[$\bullet$] Our experiments on zero-short learning show that the MAC model has poor performance in line with
	the other models in the literature.
	\item[$\bullet$] With fine-tuning, the MAC model matches state of
	the art accuracy
	\item[$\bullet$]Remains an interesting problem to investigate how we can train it to disentangle the concepts of shape and color.
	\item[$\bullet$] Experiments can be reproduced by following the \textbf{mi-prometheus}  documentation
\end{description}

@@

	\begin{figure}[H]
	\centering
				\includegraphics[width=0.60\textwidth]{../img/fail_mac_cogent_b_shape.png}
